---
title: "The grammar of graphics"
output: html_document
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)  # For ggplot, dplyr, and friends

penguins <- read_csv("data/penguins.csv")  # Load data
```

## Figuring out what's in the data

```{r}
penguins
```

## Your Turn 2

Add `color`, `size`, `alpha`, or `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, 
                           y = body_mass_g, 
                           color = species))
```

## Your Turn 3

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(penguins) +
  geom_point(aes(x = species, y = body_mass_g))
```

## Your Turn 4

Make a histogram of the `bill_length_mm` variable from `penguins`.

```{r}
ggplot(data = penguins) 
```

## Your Turn 5

Make a density plot of `bill_length_mm` filled by `species`.

```{r}
ggplot(data = penguins) 
```

## Your Turn 6

Predict what this code will do. Then run it.

```{r}
ggplot(data = penguins) +
  geom_point(mapping = aes(x = body_mass_g, 
                           y = bill_depth_mm, 
                           color = species)) +
  geom_smooth(mapping = aes(x = body_mass_g, 
                            y = bill_depth_mm, 
                            color = species))
```

## Your Turn 7

Make a density plot of `bill_length_mm` filled by `species`. *Use the viridis fill scale.*

```{r}
ggplot(data = penguins) 
```

## Your Turn 8

Facet this scatterplot by `island`. Are there any interesting trends?

```{r}
ggplot(penguins, 
       aes(x = body_mass_g, y = bill_length_mm, color = species)) +
  geom_point()
```
